\documentclass[12pt,a4paper]{moderncv}
\usepackage{enumitem}

% moderncv themes
\moderncvtheme[red]{classic}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\addpenalty{-1000}

%\setlist[enumerate, 1]{leftmargin=\separatorrulewidth}

% adjust the page margins
\usepackage[scale=0.9]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\titlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{\newline{\slshape#4}}%
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{\newline #6}%
    \strut%
    \ifx&#7&%
    \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

% personal data
\firstname{Pedro}
\familyname{Montoto García}
\title{Technical Game Designer}               % optional, remove the line if not wanted
%\address{}    % optional, remove the line if not wanted
\mobile{+34 620 575581}                    % optional, remove the line if not wanted
%\phone{+34 620 575581}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{pmgberm@gmail.com}                      % optional, remove the line if not wanted
%\email{\href{mailto:s.dakourou@gmail.com}{s.dakourou@gmail.com}}                      % optional, remove the line if not wanted
\social[linkedin][http://bit.ly/pedros-linkedin]{pedromontoto}               % optional, remove the line if not wanted
\social[github][http://bit.ly/pedros-github]{McOmghall}               % optional, remove the line if not wanted
%¡\extrainfo{} % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

A \textbf{Game Designer} and \textbf{Tools Developer} with a \textbf{diverse professional experience} in the fields of finance, data analysis, machine learning and web development. 

My main game development experience is with the \textbf{Unreal Engine}. Due to my gamedev work I had to jump into different disciplines to support the team, and so I had to learn on the fly basic animation, 3D modelling and shading, VFX, and sound design, as needed. I also have some knowledge of \textbf{Unity} and have worked with some general purpose programming languages including \textbf{C++}, \textbf{JavaScript} and \textbf{Java}.

(Updated: \today)

\section{Qualities}
\begin{itemize}[label={}, leftmargin=\hintscolumnwidth+\separatorcolumnwidth]
	\setlength{\itemsep}{.12em}
	\item Strong analytical, problem-solving and communication skills
	\item Eager to learn and adaptable
	\item Experience in programming and project management techniques and tools
	\item Experience with data analysis to drive business processes
	\item Speaks 4 languages fluently and wants to learn more
	\item Worked in different parts of Spain, Luxembourg, Sweden and Great Britain
\end{itemize}

\section{Selected Recent Works}
\cventry{Jun 2018 \\ Nov 2018}{OVERKILL's The Walking Dead}{Full Game, as Technical Designer}{}{\url{http://bit.ly/otwd-pedro}}{OVERKILL's The Walking Dead is a four player co-op action FPS where you fight the dead as well as the living. Set in The Walking Dead Universe, you and your group try to survive in a post-apocalyptic Washington D.C.\\
Credited as Technical Designer, worked primarily with the Level Design team, building level objects and systems and acting as liaison between creative and technical team members.
}

\cventry{Mar 2019}{Time Enhancements UE4 Plugin}{UE4 Editor Plugin - BP Extension}{}{\url{https://github.com/McOmghall/time-enhancements-UE4-plugin}}{Built during free time to research how to add new functionality to the existing BP editor in UE4. This editor extension adds a few BP-friendly Timer handlers for common tasks like prototyping timed transitions and other time-related tasks. It includes a fully-customizable generic State Machine that can be used for any project (both Single Player and on the network) to encapsulate states in game objects, simplifying prototyping. This plugin is currently used at Starbreeze Studios.}

\cventry{Jun 2019 \\ Jul 2019}{Procedural Terrain Generation UE4 Plugin}{UE4 Editor Plugin - Terrain Generation}{}{\url{https://github.com/McOmghall/procedural-terrain-generator-UE4-plugin}}{Built during free time as a proof-of-concept for a PTG architecture that integrates with Unreal standard systems. It works as a system of \textit{filters} that process the terrain in a given state and modify it according to their own rules. Every filter is customizable in BP and C++ and you can't write your own with the provided API.}

\newpage

\section{Experience}
\cventry{Currently \\ Dec 2019}{Game School Teacher}{Futuregames}{Stockholm, Sweden}{}{Teaching Unreal C++ and BP courses for programmers and designers in one of the main game schools in Stockholm. Also mentoring sessions for students.}

\cventry{Currently \\ Jul 2018}{Technical Game Designer}{Starbreeze}{Stockholm, Sweden}{}{Technical Designer working with the Level Design team, responsible for building level objects and related systems, coordinating with other departments (Art, code) as necessary. Technical POC for other level designers. Due to layoffs I also supported the team with Technical Art tasks, and worked on our proprietary engine on PAYDAY 2.}

\cventry{Jun 2018 \\ Nov 2017}{Independent Game Designer and Developer}{}{}{}{Developing casual arcade games as a Technical Game Designer within a team of 14 people. One of our games, Sea Bubble, is realeased on Steam: \url{https://store.steampowered.com/app/1103310/Sea_Bubble/}}

\cventry{Nov 2017 \\ Sep 2016}{Game Design Student}{U-Tad}{Madrid}{}{Worked for a 16 people team (5 designers, 5 artists and 6 programmers) as a game designer developing our common master's capstone project. Also took part in Global Game Jam in Madrid.}

\cventry{Sep 2016\\May 2011}{Software Engineer}{Multiple companies}{Europe}{}{Worked for the logistics and e-commerce (Amazon), banking (Indra and Bankia), machine learning research (Universidade de Santiago de Compostela and Universidade da Coruña), and business intelligence industries. \\ 
Developed mostly webpages, but also proof-of-concept systems based on new research and data analytics services. \\
Lead and coached junior team members. \\
Also contributed to a number of Open Source projects (http://bit.ly/pedros-github).
}

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{2016 - 2017}{Master's Degree in Game Design, {\normalfont \textit{7.6/10}}}{U-Tad}{Madrid}{}{Game Design and Development, Final project: Hack and Slash game (Darkborn)}
\cventry{2011 - 2016}{Master's Degree in Logic and the Philosophy of Science, {\normalfont \textit{7.0/10}}}{Universidade de Santiago de Compostela}{}{}{Cognitive Psychology, Metamathematics, Rationality, Microeconomics, Argumentation Theory and Artificial Intelligence}
\cventry{2007 - 2011}{Bachelor's Degree in Computer Science, {\normalfont \textit{6.4/10}}}{Universidade de Santiago de Compostela}{}{}{Software Engineering, Project Management, Network and Systems administration, Optimization, Artificial Intelligence}

%\section{Master Thesis}
%\cvline{Title}{\emph{The concept of intelligence after Computing Machinery and Intelligence: a historical perspective}.}
%\cvline{Supervisor}{Enrique Alonso González, UAM}
%\cvline{Description}{\small An analysis on the future of the concept of intelligence from the perspective of the cognitive sciences, especially AI}
%\cvline{Paper}{\url{https://github.com/McOmghall/ml-wip/tree/master/AI_comment}}

%\section{Bachelor Thesis}
%\cvline{Title}{\emph{Library for the execution of fuzzy quantified syllogisms}}
%\cvline{Supervisors}{Alberto Bugarín Diz, Martín Pereira Fariña}
%\cvline{Description}{\small Starting as a part of a research program on optimization-based logic systems. Implemented on Java, Linear and Non-linear optimization techniques, parsing tools (ANTLR) and the PMP project management system.}
%\cvline{Paper}{\url{http://citius.usc.es/investigacion/publicacions/listado?106}}

\section{Languages}
\cvlanguage{Galician}{Native}{}
\cvlanguage{Spanish}{Native}{}
\cvlanguage{Portuguese}{Fluent}{}
\cvlanguage{English}{Fluent}{TOEFL, 108/120, License: 11069417}
\cvlanguage{Japanese}{Basic}{}

\end{document}